### 2017-06-14 sheets/talk-7/sheet-7.tex
improve exercise about cone category

\begin{exercise}[Cone category]
  Let $\mathscr{C}$ be any category. Let \texttt{Cone} be the category of cones
  in $\mathscr{C}$ over a fixed diagram.
  What are the limits of $\mathscr{C}$ in \texttt{Cone}? What are the colimits?
\end{exercise}

@@

>>>>

\begin{definition}
  {Cone Category}
  Let $\mathscr{C}$ be any category, $D : \bf{I} \to \mathscr{C}$ a diagram.
  \texttt{Cone(D)} is the category of cones in $\mathscr{C}$ over $D$.
  \begin{itemize}
  \item The objects of \texttt{Cone(D)} are cones in $\mathscr{C}$ over $D$, that is, if
    $(U \overset{f_I}{\to} D(I))_{I \in \bf{I}}$ is a cone in $\mathscr{C}$, then there is a corresponding object
    in \texttt{Cone(D)}.
  \item The morphisms of \texttt{Cone(D)} are morphisms between two cones in $\mathscr{C}$, that is,
    if $(U \overset{f_I}{\to} D(I))_{I \in \bf{I}}, (V \overset{g_I}{\to}~ D(I))_{I \in \bf{I}}$
    are two cones in $\mathscr{C}$ and there is a morphism $V \overset{m}{\to} U$, then there
    is a corresponding morphism in \texttt{Cone(D)}.
  \end{itemize}
\end{definition}

\begin{exercise}[Cone category]
  Consider an object $L \in$ \texttt{Cone(D)} that corresponds to a limit in $\mathscr{C}$ over $D$.
  What kind of object is $L$?\\
  What about an object $L' \in$ \texttt{Cone(D)} that corresponds to a colimit in $\mathscr{C}$ over $D$?
\end{exercise}

@@

\newpage
